Building a continuous benchmarking ecosystem in bioinformatics

### 2025-09-29 3_third_review/manuscript_with_tracked_changes.tex
rc, summoned the team

Traditionally, benchmarks (whether BOP or MDP) are conducted in a {\color{red} solo and} decentralized fashion, {\color{red} \sout{and typically by}}, being started by a {\color{red} single or} small number of researchers (e.g., for MDP, the new method developer) {\color{red}using their local infrastructure}. This brings some disadvantages. For example, decentralization can be hugely inefficient; researchers studying the same task would collect reference datasets and code snippets to run methods, and implement a bespoke strategy (e.g., shell scripts) to orchestrate the methods run on datasets {\color{red}without being aware that their colleagues are simultaneously undertaking similar efforts, leading to redundant and fragmented work}. Working together would mean sharing not only datasets and code snippets, but also execution environments (software but perhaps also hardware), alignment on parameters to evaluate and eventually sharing, consolidating, and interpreting results. However, because there are not many standards of how benchmarks are implemented \cite{Sonrel2023-te}, another disadvantage of decentralized benchmarks is that, while these components may eventually be openly shared as a product of a research study, the contents of a benchmark are non-interoperable, even across benchmarks of the same task. Furthermore, decentralized benchmarks have been criticized on the basis of `inflating model performance' due to decisions made in preprocessing or parameter tuning \cite{luecken2025open}; such issues could be mitigated by gathering the `wisdom of crowds' that is implicit in running centralized benchmarks.

>>>>

Traditionally, benchmarks (whether BOP or MDP) are conducted in a {\color{red} solo and} decentralized fashion, {\color{red} \sout{and typically by}}, being started by a {\color{red} single researcher or} small {\color{red}\sout{number of researchers}team} (e.g., for MDP, the new method developer) {\color{red}using their local infrastructure}. This brings some disadvantages. For example, decentralization can be hugely inefficient; researchers studying the same task would collect reference datasets and code snippets to run methods, and implement a bespoke strategy (e.g., shell scripts) to orchestrate the methods run on datasets {\color{red}without being aware that their colleagues are simultaneously undertaking similar efforts, leading to redundant and fragmented work}. Working together would mean sharing not only datasets and code snippets, but also execution environments (software but perhaps also hardware), alignment on parameters to evaluate and eventually sharing, consolidating, and interpreting results. However, because there are not many standards of how benchmarks are implemented \cite{Sonrel2023-te}, another disadvantage of decentralized benchmarks is that, while these components may eventually be openly shared as a product of a research study, the contents of a benchmark are non-interoperable, even across benchmarks of the same task. Furthermore, decentralized benchmarks have been criticized on the basis of `inflating model performance' due to decisions made in preprocessing or parameter tuning \cite{luecken2025open}; such issues could be mitigated by gathering the `wisdom of crowds' that is implicit in running centralized benchmarks.
